---
title       : Interactive Clustering Application
subtitle    : Built with Shiny by RStudio with Iris Data
author      : Olivia Zhao
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Idea Generation

### When building clusteirng models, does it bother you when you are facing the scenarios below?

1. Tune the parameters a lot of times to get an ideal result
2. Regenerate the visualizations every time with a new model
3. Compare different model results seperately

--- .class #id 

## To Make Life Easier with Clustering

### We have built an application:

1. Allowing users to manipulate number of clusters and sample size selected for visualization
2. With interactive visualization automatically refreshed when parameters are updated
3. Incorporating two clustering methods for easier comparison

--- .class #id 

## Iris Data Clustering
K-means clustering confusion matrix: 3 clusters
```{r,echo=FALSE,results='markup'}
# k-means clustering
data <- iris
data$Species <- NULL
km <- kmeans(data,3)
table(iris$Species,Cluster=km$cluster)
```
Hierarchical clustering confusion matrix: 3 clusters
```{r,echo=FALSE,results='markup'}
# hierarchical clustering
hc <- hclust(dist(data),method="ave")
groups <- cutree(hc,k=3)
table(iris$Species,Cluster=groups)
```     
The above results show that cluster 'Setosa' can be easily seperated from the other two clusters, and that clusters 'Versicolor' and 'Virginica' are to a small degree overlapped with each other.

--- .class #id 

## Usage and Improvement

### Usage

The application can be used on other datasets with/without class labels for exploring purpose. It will be a good application in customer segmentation and allow user to get a quick answer via visualization. 

### Improvement

1. Add data exploratory summary and visualization
2. Add supervised learning analysis





